Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-11-20 analysis/paper/paper.qmd
changed fig 4 to boxplot

```{r}
#| label: fig-tcsa-raw-materials
#| fig-cap: "Histograms of TCSA values by lithic raw material."
#| fig-width:   4.5
#| fig-height:  4

# Facet by raw materials
 ggplot(tcsa_raw,
              aes(min_tcsa, 
                  fill = n)) +
  geom_histogram() +
  theme_bw(base_size = 6) +
  labs(x = "TCSA", 
       y = "Count of artefacts") +
  facet_wrap(~label_raw,
                  scales = "free_y",
                  ncol = 1)  +
  scale_fill_viridis_c(name = "Number\nof artefacts") +
  annotate("rect", 
           xmin = 4,
           xmax = 18,
           ymin = 0,
           ymax = 2.5,
           fill = "green",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Poisoned\narrow tips",
               hjust = 0,
               lineheight = 0.75,
           y = (0+2.5)/2,
           x = 5.5) +
      annotate("rect", 
           xmin = 17,
           xmax = 47,
           ymin = 2.5,
           ymax = 5,
           fill = "blue",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Un-poisoned\narrow tips",
               hjust = 0,
               lineheight = 0.75,
           y = (2.5+5)/2,
           x = 28) +
      annotate("rect", 
           xmin = 40,
           xmax = 76,
           ymin = 5,
           ymax = 7.5,
           fill = "orange",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Dart tips",
               hjust = 0,
           y = (5+7.5)/2,
           x = 53) +
      annotate("rect", 
           xmin = 42,
           xmax = 90,
           ymin = 7.5,
           ymax = 10,
           fill = "purple",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Javelin tips",
               hjust = 0,
           y = (7.5+10)/2,
           x = 70) +
     annotate("rect", 
           xmin = 80,
           xmax = 200,
           ymin = 10,
           ymax = 12.5,
           fill = "yellow",
           alpha = 0.2) +
      annotate("text", 
               label = "Stabbing spear tips",
               size = point_function_group_label_size,
               hjust = 0,
           y = (10+12.5)/2,
           x = 160)

@@

```{r}
#| label: fig-tcsa-per-sites
#| fig-cap: "Histograms of TCSA values by archaeological site."
#| fig-width:   4.5
#| fig-height:  4

>>>>

```{r}
#| label: fig-tcsa-raw-materials
#| fig-cap: "TCSA values by lithic raw material."
#| fig-width:   4.5
#| fig-height:  4

 ggplot(tcsa_raw,
              aes(y = min_tcsa, 
                  x = label_raw)) +
  geom_boxplot() +
  theme_minimal() +
  labs(x = "", 
       y = "TCSA") +
  theme(axis.text.x = element_text(size = 6)) +
  scale_x_discrete(guide = guide_axis(angle = 45))+
  geom_quasirandom(alpha = 0.4,
                   size = 2.3)

@@

```{r}
#| label: fig-tcsa-per-sites
#| fig-cap: "TCSA values by archaeological site."
#| fig-width:   4.5
#| fig-height:  4
